The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-10-22 manuscript/manuscript.qmd
Implement lineplot scaling for unavoidable cases in manuscript

```{julia}
#| fig-cap: "The number of unavoidable cases of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-unavoidable
line_plot(
    optimal_threshold_characteristics;
    outcome = :unavoidable_cases,
    ylabel = "Unavoidable Cases",
    facet_fontsize = 18,
    labelsize = 20,
    show_x_facet_label = true,
    show_y_facet_label = false,
    ylims = (0, 3.5e4),
    force = true,
    save_plot = false,
    clinical_hline = clinical_hline,
)
```

>>>>

```{julia}
#| fig-cap: "The number of unavoidable cases of outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-unavoidable
line_plot(
    optimal_threshold_characteristics;
    outcome = :unavoidable_cases,
    ylabel = "Unavoidable Cases",
    facet_fontsize = 18,
    labelsize = 20,
    show_x_facet_label = true,
    show_y_facet_label = false,
    ylims = (0, 2.4e4),
    force = true,
    save_plot = false,
    clinical_hline = clinical_hline,
    cases_scaling = gha_2022_scale_population_per_annum
)
```
